---
title: "Forecast"
output: html_document
params:
  Infected: NA
  Recovered: NA
  Deceased: NA
  Country: NA
  DownloadDate: NA
  ForecastDates: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(plotly)
library(tidyverse)
library(lubridate)
```

## Forecast Data from `r params$Country`, `r params$DownloadDate`
### Plot Output

This report contains Forecast data for the selected Country and delivers an Overview about the Forecast. Hereinafter, the forecast data from the corresponding data are shown in the graphs below:
```{r Infected, echo=FALSE}
plot_ly(data = params$Infected)%>%
  add_lines(x = ~params$ForecastDates, y = ~round(params$Infected$"Point Forecast",digits = 0), color = I("blue"), name = "prediction")%>%
  add_ribbons(x = ~params$ForecastDates, ymin = ~round(params$Infected$"Lo 95",digits=0), ymax = ~round(params$Infected$"Hi 95", digits = 0), color=I("gray95"), name ="95% confidence")%>%
  add_ribbons(x = ~params$ForecastDates, ymin = ~round(params$Infected$"Lo 80",digits=0), ymax = ~round(params$Infected$"Hi 80", digits = 0), color=I("gray80"), name ="80% confidence")%>%
  layout(title="Forecast Infected Cases", xaxis=list(title="Date"),yaxis=list(title="Infected"))
```

```{r Recovered, echo=FALSE}
plot_ly(data = params$Recovered)%>%
  add_lines(x = ~params$ForecastDates, y = ~round(params$Recovered$"Point Forecast",digits = 0), color = I("blue"), name = "prediction")%>%
  add_ribbons(x = ~params$ForecastDates, ymin = ~round(params$Recovered$"Lo 95",digits=0), ymax = ~round(params$Recovered$"Hi 95", digits = 0), color=I("gray95"), name ="95% confidence")%>%
  add_ribbons(x = ~params$ForecastDates, ymin = ~round(params$Recovered$"Lo 80",digits=0), ymax = ~round(params$Recovered$"Hi 80", digits = 0), color=I("gray80"), name ="80% confidence")%>%
  layout(title="Forecast Recovered Cases", xaxis=list(title="Date"),yaxis=list(title="Recovered"))
```

```{r Deceased, echo=FALSE}
plot_ly(data = params$Deceased)%>%
  add_lines(x = ~params$ForecastDates, y = ~round(params$Deceased$"Point Forecast",digits = 0), color = I("blue"), name = "prediction")%>%
  add_ribbons(x = ~params$ForecastDates, ymin = ~round(params$Deceased$"Lo 95",digits=0), ymax = ~round(params$Deceased$"Hi 95", digits = 0), color=I("gray95"), name ="95% confidence")%>%
  add_ribbons(x = ~params$ForecastDates, ymin = ~round(params$Deceased$"Lo 80",digits=0), ymax = ~round(params$Deceased$"Hi 80", digits = 0), color=I("gray80"), name ="80% confidence")%>%
  layout(title="Forecast Deceased Cases", xaxis=list(title="Date"),yaxis=list(title="Deceased"))
```

### Table Output

In this segment you will see the data visualized in different tables.

#### Infected Measures Table
````{r Preparation, echo = FALSE}
    val <- params$ForecastDates
    val2 <- as.POSIXct(val, origin="1970-01-01")
```

```{r Infected_Table, echo=FALSE}
plot_ly(type = 'table',
        header = list(
          values = c("Date","Infected Mean","Infected Low 80% Confidence","Infected High 80% Confidence","Infected Low 95% Confidence","Infected High 95% Confidence"),
          align = c("center","center")
        ),
        cells = list(
          values = rbind(
            val2,
            round(params$Infected$"Point Forecast", digits = 0),
            round(params$Infected$"Lo 80", digits = 0),
            round(params$Infected$"Hi 80", digits = 0),
            round(params$Infected$"Lo 95", digits = 0),
            round(params$Infected$"Hi 95", digits = 0)
          ),
          align = c('left','center')
        ))
```

#### Recovered Measures Table


```{r Recovered_Table, echo=FALSE}
plot_ly(type = 'table',
        header = list(
          values = c("Date","Recovered Mean","Recovered Low 80% Confidence","Recovered High 80% Confidence","Recovered Low 95% Confidence","Recovered High 95% Confidence"),
          align = c("center","center")
        ),
        cells = list(
          values = rbind(
            as.Date(params$ForecastDates),
            round(params$Recovered$"Point Forecast", digits = 0),
            round(params$Recovered$"Lo 80", digits = 0),
            round(params$Recovered$"Hi 80", digits = 0),
            round(params$Recovered$"Lo 95", digits = 0),
            round(params$Recovered$"Hi 95", digits = 0)
          ),
          align = c('left','center')
        ))
```

#### Deceased Measures Table

```{r Deceased_Table, echo=FALSE}
plot_ly(type = 'table',
        header = list(
          values = c("Date","Deceased Mean","Deceased Low 80% Confidence","Deceased High 80% Confidence","Deceased Low 95% Confidence","Deceased High 95% Confidence"),
          align = c("center","center")
        ),
        cells = list(
          values = rbind(
            val2,
            round(params$Deceased$"Point Forecast", digits = 0),
            round(params$Deceased$"Lo 80", digits = 0),
            round(params$Deceased$"Hi 80", digits = 0),
            round(params$Deceased$"Lo 95", digits = 0),
            round(params$Deceased$"Hi 95", digits = 0)
          ),
          align = c('left','center')
        ))
```